Development of Physics or HPC Optimisation of a parallel 2D lattice Boltzmann solver using GPUs/CUDA

### 2017-08-13 Thesis/Draft.tex
working

\subsubsection{Final version v1.1}
\subsubsection{High order color gradient}
\subsubsection{CUDA compute capability}
\subsection{Hardware}
\subsection{Double vs Single}
\chapter{Conclusions}

>>>>

\subsubsection{Final version v1.1}
We then applied the same changes that were applied in the 2D model. We unrolled the loops inside the kernel calls and improved the way that the distribution function was being calculated. All of these changes were done together since we knew from the 2D model that they had a positive effect on the final result. In this version, we did not test the manually unrolled loops. No matter how good the performance could be (which should be a couple of seconds more), Figure \ref{fig:unrollComp} shows how much worse the code gets when this technique is used for this model, even more so if we take into account that from 2D to 3D the loops increase from 9 iterations to 19, making it even harder to manually unroll them.

  \begin{figure}[H]
  	\centering
  	\includegraphics[width=\linewidth]{Resources/Images/vfv3d.png}
  	\caption{Runtime comparison between the final version and version 1.0}
  	\label{fig:vfv3d}
  \end{figure}

\subsubsection{High order color gradient}
\subsubsection{CUDA compute capability}
\subsection{Hardware}
\subsection{Double vs Single}
\chapter{Conclusions}
